A warm sub-Neptune transiting a Solar twin in TESS

### 2019-09-30 paper/ms.tex
Updates from Overleaf
more detailed outline

%The Transiting Exoplanet Survey Satellite (\TESS) has detected over one thousand candidate exoplanets to date. (blah blah)

@@

\section(Data)
\label{s:data}

@@

(about \HARPS \RVs)

@@

@@

@@

>>>>

The Transiting Exoplanet Survey Satellite (\TESS) has detected over one thousand candidate exoplanets to date. 
The majority of these newly discovered planets orbit bright, nearby stars, making them perfectly suited for follow-up observations, including mass measurements and atmospheric spectroscopy.

%All

@@

\section{Data}
\label{s:data}

@@

(about \HARPS\ \RVs)

@@

\subsection{Gaia}

(cross-match. nearby stars?)

@@

(transits visible by eye, TOI flagging)

(centroid analysis?)

(GP model \& discussion of physical meaning - is this rotation period?)

(results of planet-only fit)

@@

(\HARPS\ upgrade offset)

(what do logRHK, BIS, FWHM correlations look like \& their periodograms after removing this offset (\& maybe low-pass filtering??))

(periodogram analysis of RVs (maybe after subtracting off activity trends))

(adding a planet to the model)

(evidence for additional periods?)
